Postratification Code

### 2019-10-21 Code/postratification_code.Rmd
commit

vote_yes <- c(rep(0, 25*(1-0.76)), 
              rep(1, 25*0.76),
              rep(0, 50*(1-0.3)),
              rep(1, 50*0.3))
vote_yes

@@

>>>>

vote_yes <- c(rep(0, 25*(1-0.76)), 
              rep(1, 25*0.76),
              rep(0, 50*(1-0.3)),
              rep(1, 50*0.3))
vote_yes
mean(vote_yes)

@@

That is our population. We will now make a sample with subgroups.

```{r}
poll_data <- tibble(
  group = c(rep("A", 25), rep("B", 10)),
  yes = c(rep(1, 19), rep(0, 6), rep(1, 3), rep(0, 7))
)
poll_data %>%
  group_by(group) %>%
  summarise(count = n())
```

Here are our subgroups and how many our represented in our sample. It does not match the proportions found in our population.

```{r}
Census <- tibble(
  group = c("A", "B"),
  pop = c(25, 50)
)
Census
mean(poll_data$yes)
```

Our mean for the sample varies from our population, so we stratify.

```{r}
group_support <- poll_data %>%
  group_by(group) %>%
  summarise(perc_support = mean(yes))
group_support

overall_support <- group_support %>%
  summarise(total_support = sum(perc_support * Census$pop/sum(Census$pop)))
overall_support
```
